---
title: "MA429 MOCK PROJECT"
output: MA429_html_notebook
---

```{r}
test <- read.table("http://mlr.cs.umass.edu/ml/machine-learning-databases/adult/adult.test", skip=1, 
                   sep=",", header = FALSE,
                   col.names=c("Age", "Workclass", "Fnlwgt","Education","Education-num","Marital-status",
                               "Occupation","Relationship","Race","Sex",
                               "Capital-gain","Capital-loss","Hours-per-week","Native-country","Income-level"))
train <- read.table("http://mlr.cs.umass.edu/ml/machine-learning-databases/adult/adult.data", skip=1, 
                   sep=",", header = FALSE,
                   col.names=c("Age", "Workclass", "Fnlwgt","Education","Education-num","Marital-status",
                               "Occupation","Relationship","Race","Sex",
                               "Capital-gain","Capital-loss","Hours-per-week","Native-country","Income-level"))
```


```{r}

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
